Dismal Code: Studying the Evolution of Security Bugs

### 2013-03-10 docs/msr.tex
updated numbers in data provenance

\author{
\IEEEauthorblockN{Dimitris Mitropoulos\IEEEauthorrefmark{1}, Vassilios Karakoidas\IEEEauthorrefmark{1},
Georgios Gousios\IEEEauthorrefmark{2}, Panagiotis Louridas\IEEEauthorrefmark{1},
Diomidis Spinellis\IEEEauthorrefmark{1}}\\
\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Management Science and Technology\\
Athens University of Economics and Business\\
\{dimitro, bkarak, louridas, dds\}@aueb.gr}\\
\IEEEauthorblockA{\IEEEauthorrefmark{2}TODO: Add Affiliation here\\
Delft University of Technology\\
G.Gousios@tudelft.nl}}

@@

\begin{table}
\centering
\caption{Descriptive Statistics Measurements for the Maven Repository}
\label{tbl:repository}
\begin{tabular}{l r}
\hline
Measurement & Value\\
 \hline
Projects & 17,505\\
Versions (total) & 114,399\\
Min & 1\\
Max & 337\\
Mean & 6.54\\
Median & 3\\
Range & 336\\
1$^{st}$ Quartile & 1\\
3$^{rd}$ Quartile & 8\\
\hline
\end{tabular}
\end{table}

@@

In addition, we implemented a series of audits in the worker scripts that
checked if the {\sc jar}s are valid in terms of implementation. For instance,
for every {\sc jar} the worker checked if there were any {\it .class} files
before invoking FindBugs. After the project filtering we narrowed down
our data set to 17,055 projects with 114,399 versions.
Table~\ref{tbl:repository} summarises the data set information and
provides the basic descriptive statistic measurements. The distribution of version
count among the selected projects is presented in Figure \ref{fig:version-count}.

@@

The statistical mesurements presented in Table~\ref{tbl:repository}
indicate that we have 17,505 projects and the data set's median
is 3, which means that almost 50\% (8,753 projects) of the project
population has 1 to 3 versions.
Note that the Maven repository has many projects with a
few number of versions. For instance, there are numerous projects with a
number of versions that is less than ten.
There are a few projects containing ten
versions and only a few with hundreds of versions. The maximum number of
versions for a project is 337. The 3$^{rd}$ quartile measurement
also indicated that 75\% (13,129) of the projects have a maximum of 8 versions.

>>>>

\author{
\IEEEauthorblockN{Dimitris Mitropoulos\IEEEauthorrefmark{1}, Vassilios Karakoidas\IEEEauthorrefmark{1},
Georgios Gousios\IEEEauthorrefmark{2}, Panagiotis Louridas\IEEEauthorrefmark{1},
Diomidis Spinellis\IEEEauthorrefmark{1}}\\
\IEEEauthorblockA{\IEEEauthorrefmark{1}Department of Management Science and Technology\\
Athens University of Economics and Business\\
\{dimitro, bkarak, louridas, dds\}@aueb.gr}\\
\IEEEauthorblockA{\IEEEauthorrefmark{2}
Software Engineering Research Group\\
Delft University of Technology\\
G.Gousios@tudelft.nl}}

@@

\begin{table}
\centering
\caption{Descriptive Statistics Measurements for the Maven Repository}
\label{tbl:repository}
\begin{tabular}{l r}
\hline
Measurement & Value\\
 \hline
Projects & 17,505\\
Versions (total) & 115,214\\
Min & 1\\
Max & 338\\
Mean & 6.58\\
Median & 3\\
Range & 337\\
1$^{st}$ Quartile & 1\\
3$^{rd}$ Quartile & 8\\
\hline
\end{tabular}
\end{table}

@@

In addition, we implemented a series of audits in the worker scripts that
checked if the {\sc jar}s are valid in terms of implementation. For instance,
for every {\sc jar} the worker checked if there were any {\it .class} files
before invoking FindBugs. After the project filtering we narrowed down
our data set to 17,055 projects with 115,214 versions.
Table~\ref{tbl:repository} summarises the data set information and
provides the basic descriptive statistic measurements. The distribution of version
count among the selected projects is presented in Figure \ref{fig:version-count}.

@@

The statistical mesurements presented in Table~\ref{tbl:repository}
indicate that we have 17,505 projects and the data set's median
is 3, which means that almost 50\% (8,753 projects) of the project
population has 1 to 3 versions.
Note that the Maven repository has many projects with a
few number of versions. For instance, there are numerous projects with a
number of versions that is less than ten.
There are a few projects containing ten
versions and only a few with hundreds of versions. The maximum number of
versions for a project is 338. The 3$^{rd}$ quartile measurement
also indicated that 75\% (13,129) of the projects have a maximum of 8 versions.
